The course covers (parts of) the \addindex{chapters}:

\begin{description}
  \item [Ch 5] \addindex{MOSFET} \\
               5.1 Device structure and physical operation \\
               5.2 \addindex{Current-voltage characteristics} \\
               5.3 MOSFET circuits at \addindex{DC} \\
               TODO only these?
  \item [Ch 6] \addindex{BJT} \\
               6.2 Current-voltage characteristics \\
               6.3 \addindex{BJT} circuits at DC \\
               TODO only these? \\
               TODO fuck BJT?
  \item [Ch 7] \addindex{Transistor Amplifiers} \\
               7.3 Basic configurations \\
               7.4 \addindex{Biasing} \\
               7.5 Discrete-circuit amplifiers \\
               7.6 Doesn't exist. Wtf dr. proffesor \\
               TODO only these?
  \item [Ch 8] Building blocks of \addindex{IC Amplifiers} \\
               8.1 IC design philosophy \\
               TODO not 8.2? \\
               8.3 The basic gain cell \\
               8.4 Common-gate and common-base amplifiers \\
               8.5 Cascode amplifiers \\
               TODO only these?
  \item [Ch 9] \addindex{Differential Amplifiers}
               9.1 MOS differential pair \\
               9.2 BJT differential pair \\
               9.3 Common-mode rejection \\
               9.5 Differential amplifier with current-mirror load \\
               9.7 Doesn't exist. WTF! \\
               and \addindex{Multistage Amplifiers}
               TODO only these?
  \item [Ch 15] Advanced Topics in \addindex{Digital IC Design}
               15.1 Implications of technology scaling \\
               15.2 Digital IC technologies, logic-circuit families,
                    design methodologies \\
               15.3 \addindex{Pseudo-NMOS} logic circuits \\
               15.4 Pass-transistor logic circuits \\
               TODO only these?
\end{description}

TODO subchapter names

\paragraph{Ch 5 - MOSFET} \hfill \\
The books chapter covers:
\begin{itemize}
  \item How MOS \addindex{transistors} work and are physically build
  \item How current through one \addindex{terminal} is controlled by voltage
        over two other terminals.
  \item Designing and analyzing circuits with MOSFET, resistors and dc sources.
\end{itemize}

\paragraph{Ch 6 - BJT} \hfill \\
The books chapter covers:
\begin{itemize}
  \item How BJTs work and are physically built.
  \item How voltage on two terminals control current in the third terminal.
  \item Designing and analyzing circuits with BJT, resistors and dc sources.
\end{itemize}

\paragraph{Ch 7 - Transistor Amplifiers} \hfill \\
The books chapter covers:
\begin{itemize}
  \item How to make an \addindex{amplifier} with MOSFET or BJT
  \item Making \addindex{linear amplifiers} from non-linear transistors
  \item Using \addindex{equivalent circuits} to model
        \addindex{linear operation} of transistor around bias point
  \item Three basic ways to make amplifiers from transistors
  \item Practical transistor amplifier circuits from
        \addindex{discrete components}
\end{itemize}

\paragraph{Ch 8 - } \hfill \\
The books chapter covers:
\begin{itemize}
  \item How IC \addindex{philosophy} differs from
        \addindex{discrete-circuit} design
  \item \addindex{Biasing} IC amps with \addindex{current sources} and
        replicating reference currents with current mirrors.
  \item Basic gain cells: \addindex{CS} and \addindex{CE} amps with
        current-source loads
  \item CG and CB amps as \addindex{current buffers}
  \item Increasing gain with \addindex{cascoding}
  \item Designing and analyzins cascode amps and
        \addindex{cascode current sources}
  \item \emph{Ingenious} techniques improving current mirrors
  \item Multi-stage amps with multiple transistors
\end{itemize}

\paragraph{Ch 9 - } \hfill \\
The books chapter covers:
\begin{itemize}
  \item MOS differential amps: rejecting \addindex{common-mode} noise,
        amplifying \addindex{differential signals}
  \item Designing and analyzing MOS \addindex{differential amps}
  \item Differential amps with: \addindex{passive resistive loads}, 
  \item Popular and \emph{ingenious} differential amp with current-mirror load
  \item Structure, analysis and design of \addindex{multi-stage} amps in cascade
\end{itemize}

\paragraph{Ch 15 - } \hfill \\
The books chapter covers:
\begin{itemize}
  \item Technology scaling: Moores law and deep-submicron
  \item Why CMOS is dominant
  \item Pseudo nMOS: Single \addindex{pMOS} \addindex{PUL}
        (\addindex{pull-up network}) and high fan-in gates.
  \item \addindex{Pass-transistor logic}
  \item \addindex{Transmission gate} from parallel pMOS and nMOS
  \item \addindex{Dynamic logic}: Replacing pull-up network with spooky shit
  \item \addindex{Emitter-coupled logic}: fast ass shit
  \item \addindex{BiCMOS}: Combining MOSFET and BJT
\end{itemize}

TODO don't itemize
